### 2016-12-09 poster/poster.tex
added a bunch on the poster

\documentclass[paperwidth=118cm,paperheight=84cm,portrait,margin=8em,fontscale=0.3]{baposter}
%\usepackage{acl-hlt2011}
%84 cm wide x 118 cm high
\usepackage{times}
\usepackage{svg}
\usepackage{color}
\usepackage{multirow}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{setspace}

@@

\begin{poster}{
	%grid=true,
	columns=3,
	colspacing=2em,
	headerheight = 0.17\textheight ,
	%eyecatcher=false, 
	borderColor=uwMetallicGold,
	headerColorOne=uwPurple,
	headerColorTwo=uwPurple,
	headerFontColor=white,
	% Only simple background color used, no shading, so boxColorTwo isn't necessary
	boxColorOne=white,
	boxColorTwo=uwPurple,
	headerborder=closed,
	headershape=rounded,
	headerfont=\Large\sf\bf,
	textborder=none,
	bgColorOne=uwGold,
	bgColorTwo=uwPurple,
	background=plain,
	headerborder=open,
	boxshade=plain
}
{
%Eye Catcher, empty if option eyecatcher=no
{
	\begin{tabular}{l}
			%\includegraphics[scale=.6]{graphics/pnt5in.png}
			\includegraphics[width=2.5in]{graphics/UWlogo.pdf} \\
			%\includegraphics[scale=.6]{graphics/pnt5in.png}
			%\includegraphics[scale=.6]{graphics/pnt5in.png}
	\end{tabular}
	%\includegraphics[scale=1.7]{graphics/pnt5in.png}
}
}
{ % GUIDE: GUI for Document Exploration
\textbf{$\spadesuit$ SPADE -- SPan Annotated Document Exploration $\spadesuit$}
}
{
\vspace*{0.8em}
\textbf{Lucy Lin, George Mulcaire \& Maarten Sap}\\

%\vspace*{0.5em}
CSE 512 Data Visualization Final Project\\
Computer Science and Engineering, University of Washington

 \vspace*{6pt}
}
{
	\begin{tabular}{r}
			\includegraphics[width=1.80in]{graphics/CSElogo.png}\includegraphics[scale=.7]{graphics/pnt5in.png}
	\end{tabular}
}

@@

%% Box 0
\headerbox{Deep Learning and NLP}{name=intro1,column=0,row=0.00, span=1}{
\color{black}
\vspace*{5pt}
\textbf{NLP for NLP}
\begin{itemize}\addtolength{\itemsep}{-0.25\baselineskip}
\item nlp is natural
\item the natural is about the processing, not the language
\end{itemize}\vspace*{5pt}

\begin{tabular}{cc}
\includegraphics[width=.24\columnwidth]{graphics/python.png}
\hspace*{20pt} & \hspace*{-15pt}\parbox{0.62\textwidth}{
\vspace*{-40pt}\textbf{Deep learning}
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
\item wow
\item neurons
\item just a function
\item such deep
\vspace*{-5pt}
\end{itemize}}
\end{tabular}
}

%% Box 2
\headerbox{Dataset}{name=intro1,column=0,row=0.40, span=1}{
\color{black}
English GigaWord corpus (LDC), LA Times from 2009 ? \vspace*{10pt}
\\
\begin{tabular}{cc}
\parbox{0.45\textwidth}{
\vspace*{-0pt}
\includegraphics[width=.24\columnwidth]{graphics/newspaper.pdf}
\includegraphics[width=.24\columnwidth]{graphics/LAtimes.jpeg}

}
&
\hspace*{-10pt}
\parbox{0.50\textwidth}{
\textbf{Data}
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
\item Split into sentences then words using NLTK
\item $1,191,848$ sentences
\item $27,269,856$ words (``tokens'') total
\item $35,642$ distinct words in the end
%\vspace*{-5pt}
\end{itemize}}
\end{tabular}
}

%% Box 2
\headerbox{Hyper params?}{name=intro1,column=0,row=0.75, span=1}{
\color{black}
??
\vspace{.4pt}
}

@@

%% BOX 0
\headerbox{Logos \& Graphs}{name=results,column=1,row=0.00, span=2}{
\includegraphics[width=.24\columnwidth]{graphics/TensorFlow.png}
\includegraphics[width=.24\columnwidth]{graphics/Theano.jpeg}
\includegraphics[width=.24\columnwidth]{graphics/DyNet.pdf}
}

@@

%% BOX 0
%\headerbox{Search Results}{name=results,column=2,row=0, span=1}{
%\begin{center}
%\includegraphics[scale=.5]{graphics/searchResults.JPG}
%
%\end{center}
%\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}%\addtolength{\itemindent}{-5pt}
%\item Search for words or phrases in the document text
%\item Filter on frames to examine relationships between the language used and the frame evoked
%\item Search via the wordcloud, the search bar, or by clicking on frames in search results
%\end{itemize}
%}

>>>>

\documentclass[paperwidth=118cm,paperheight=84cm,portrait,margin=8em,fontscale=0.3]{baposter}
%\usepackage{acl-hlt2011}
%84 cm wide x 118 cm high
\usepackage{times}
\usepackage{svg}
\usepackage{color}
\usepackage{multirow}
\usepackage{latexsym}
\usepackage{amsmath,amssymb}
\usepackage{setspace}

@@

\begin{poster}{
	%grid=true,
	columns=3,
	colspacing=2em,
	headerheight = 0.17\textheight ,
	%eyecatcher=false, 
	borderColor=uwMetallicGold,
	headerColorOne=uwPurple,
	headerColorTwo=uwPurple,
	headerFontColor=white,
	% Only simple background color used, no shading, so boxColorTwo isn't necessary
	boxColorOne=white,
	boxColorTwo=uwPurple,
	headerborder=closed,
	headershape=rounded,
	headerfont=\Large\sf\bf,
	textborder=none,
	bgColorOne=uwGold,
	bgColorTwo=uwPurple,
	background=plain,
	headerborder=open,
	boxshade=plain
}
{
%Eye Catcher, empty if option eyecatcher=no
{
	\begin{tabular}{l}
			%\includegraphics[scale=.6]{graphics/pnt5in.png}
			\includegraphics[width=2in]{graphics/UWlogo.pdf} \\
			%\includegraphics[scale=.6]{graphics/pnt5in.png}
			%\includegraphics[scale=.6]{graphics/pnt5in.png}
	\end{tabular}
	%\includegraphics[scale=1.7]{graphics/pnt5in.png}
}
}
{ % GUIDE: GUI for Document Exploration
\textbf{Benchmarking Python Deep Learning \\Frameworks on Language Modeling }
}
{
\vspace*{7pt}
\textbf{Lucy Lin, George Mulcaire \& Maarten Sap}\\

%\vspace*{0.5em}
CSE 550 Systems\\
Computer Science and Engineering, University of Washington

 \vspace*{6pt}
}
{
	\begin{tabular}{r}
	\includegraphics[scale=.6]{graphics/pnt5in.png}
	\includegraphics[width=1.4in]{graphics/CSElogo.png}
	\includegraphics[scale=.7]{graphics/pnt5in.png}
	\end{tabular}
}

@@

%% Box 0
\headerbox{Deep Learning and NLP}{name=intro1,column=0,row=0.00, span=1}{
\color{black}
\vspace*{5pt}
\textbf{Deep learning ``revolution'' in natural language processing}
\begin{itemize}\addtolength{\itemsep}{-0.25\baselineskip}
\item State-of-the-art results are achieved with neural methods \\
(e.g. machine translation, speech recognition)
\item Panoply of toolkits started emerging
\end{itemize}\vspace*{5pt}

\begin{tabular}{ccc}\hspace*{10pt}
\includegraphics[scale=.2]{graphics/pnt5in.png}\\
\includegraphics[width=.24\columnwidth]{graphics/python.jpg}
 & \parbox{0.35\textwidth}{
\vspace*{-40pt}\textbf{Python Frameworks}
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
\item TensorFlow
\item Theano
\item DyNet
\vspace*{0pt}
\end{itemize}}
& \parbox{0.2\textwidth}{\vspace*{-40pt}
\includegraphics[width=40pt]{graphics/TensorFlow.png}\vspace*{3pt}\\
\includegraphics[width=40pt]{graphics/theano.jpeg}\vspace*{-1pt}\\
\includegraphics[width=40pt]{graphics/DyNet.pdf}
}
\end{tabular}
\begin{center}
\textbf{\textit{Which of these is better when tested on a real NLP task:\\ language modeling?}}
\end{center}
}

%% Box 2
\headerbox{Dataset}{name=intro1,column=0,row=0.40, span=1}{
\color{black}\vspace*{3pt}
English GigaWord corpus (LDC), LA Times from 2009 \vspace*{10pt}
\\
\hspace*{5pt}
\begin{tabular}{cc}
\parbox{0.27\textwidth}{
\vspace*{-0pt}
%\includegraphics[width=.24\columnwidth]{graphics/newspaper.pdf}
\includegraphics[width=.24\columnwidth]{graphics/latimes.jpg}

}
&
\hspace*{-10pt}
\parbox{0.6\textwidth}{
\textbf{Data}
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
\item Split into sentences then words \\ using \texttt{NLTK}
\item $1,191,848$ sentences
\item $27,269,856$ words (``tokens'') total
\item $35,642$ distinct words in the end
%\vspace*{-5pt}
\end{itemize}}
\end{tabular}
}

%% Box 2
\headerbox{Model specifics}{name=intro1,column=0,row=0.67, span=1}{
\color{black}
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
\item Words are embedded in the hidden sized space: $\mathbb{N}^{35642} \rightarrow \mathbb{R}^{256}$.
\item Embedded words are run through the RNN: $w_i = f(w_0^{i-1},\Theta)$.
\item Cross-entropy loss is used to learn the parameters.
\end{itemize}
\begin{center}
\begin{tabular}{cc}
\textbf{hyperparam} & \textbf{value} \\\hline
RNN type & \texttt{LSTM} \\
hidden size & $256$ \\
optimizer & \texttt{AdamOptimizer} \\
learning rate & $0.003$ \\
batch size & 25 \\

\end{tabular}
\end{center}
\vspace{.4pt}
}

@@

%% BOX 0
\headerbox{Logos \& Graphs}{name=results,column=1,row=0.00, span=1}{
\includegraphics[width=.24\columnwidth]{graphics/TensorFlow.png}
\includegraphics[width=.24\columnwidth]{graphics/theano.jpeg}
\includegraphics[width=.24\columnwidth]{graphics/DyNet.pdf}
}

@@

%% BOX 0
\headerbox{Search Results}{name=results,column=2,row=0, span=1}{
%\begin{center}
%\includegraphics[scale=.5]{graphics/searchResults.JPG}
%
%\end{center}
%\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}%\addtolength{\itemindent}{-5pt}
%\item Search for words or phrases in the document text
%\item Filter on frames to examine relationships between the language used and the frame evoked
%\item Search via the wordcloud, the search bar, or by clicking on frames in search results
%\end{itemize}
}
